---
title: "Lab6"
output: html_document
---
#### 1. Create a matrix mat with 5 columns and 10 rows using matrix with random values (function rnorm(50)).
```{r}
x <-  matrix(rnorm(50),10,5)
x
```
#### 2. Find the maximum value of each column.
```{r}
apply(x, 2, max)
```
#### 3. Find the mean value of each column.
```{r}
colMeans(x)
```
#### 4. Find minimum value in each row.
```{r}
apply(x, 1, min)
```
#### 5. Sort each column of the table.
```{r}
apply(x, 2, sort)
```
#### 6. Find number of values < 0 for each column. Choose your function.
```{r}
func1 <- function(m) {
  for(i in 1:ncol(m)){
    print(m[m[,i]<0,i])
  }
}
func1(x)
```
#### 7. Display s vector with Boolean values TRUE and FALSE. TRUE if there are elements> 2 in the column, FALSE if not.
```{r}
s <- c()
for(i in 1:ncol(x)){
  if(sum(x[,i]>2)>0){
    s <- c(s,TRUE)
  }else{
    s <- c(s,FALSE)
  }
}
s
```
#### 8. Create a list list1 <- list(observationA = c(1:5, 7:3), observationB = matrix(1:6, nrow=2)). For this list find sum using function lapply.
```{r}
list1 <- list(observationA = c(1:5, 7:3), observationB = matrix(1:6, nrow=2))
lapply(list1, sum)
```
#### 9. For each element of the list1 find maximum and minimum values (range) using lapply and sapply.
```{r}
lapply(list1, max)
sapply(list1, max)
lapply(list1, min)
sapply(list1, min)
```
#### 10. For the built-in data set InsectSprays find mean count for each spray.
```{r}
data(InsectSprays)
a <- c()
for(i in levels(InsectSprays$spray)){
  a <- c(a,mean(InsectSprays[InsectSprays$spray==i,1]))
}
df1 <- data.frame(a,b=levels(InsectSprays$spray))
df1
```