---
title: "Lab4"
output: html_document
---
#### 1. What names of columns in the file?
```{r}
setwd("C:/Users/gax19/Desktop/Labs_R/Lab4_R")
hw1_data <- read.csv("hw1_data.csv", header = T, sep = ",")
names(hw1_data)
```
#### 2. Display first 6 rows of the data frame.
```{r}
head(hw1_data, 6)
```
#### 3. How many rows in data frame?
```{r}
nrow(hw1_data)
```
#### 4. Display last 10 rows of the data frame.
```{r}
tail(hw1_data,10)
```
#### 5. How many «NA» values in «Ozone» column?
```{r}
sum(is.na(hw1_data$Ozone))
```
#### 6. What the mean value of column «Ozone»? Exclude «NA» values.
```{r}
mean(hw1_data[,"Ozone"])
mean(hw1_data[,"Ozone"], na.rm = TRUE)
```
#### 7. Display a part of the data frame (subset) with values «Ozone» > 31 and «Temp» > 90. What the mean value of «Solar.R» in this data frame (subset)?
```{r}
hw1_data[hw1_data$Ozone>31 & hw1_data$Temp>90,]
mean(hw1_data[hw1_data$Ozone>31 & hw1_data$Temp>90,"Solar.R"], na.rm = TRUE)
```
#### 8. What the mean value for «Temp» for June («Month» = 6)?
```{r}
mean(hw1_data[hw1_data$Month == 6,"Temp"], na.rm = TRUE)
```
#### 9. What the maximum value for «Ozone» for May?
```{r}
max(hw1_data[hw1_data$Month == 5,"Temp"], na.rm = TRUE)
```